Methodology for Assessing the State of the Practice for Domain X

### 2020-04-16 StateOfPractice/Methodology/Methodology.tex
usability

\section{User Experiments}

Describe experiments with users to assess usability, performance etc.

>>>>

\section{User Experiments}
\subsection{Usability Experiment}
Steps:
\begin {enumerate}
\item Write research questions
\item Prepare logistic details(location, time table, recording setup, moderators etc)
\item Prepare survey questions
\item Select a list of projects
\item Design the tasks for the study subjects to perform (tasks can be defined based on user category, at least one task to modify the software)
\item Select participants
\item Conduct usability session(s) 
\item Survey the study subject to collect pre-experiment data
\item Perform tasks
\item Observe the study subjects (take notes, record sessions, watch out for body language and verbal cues)
\item Survey the study subjects to collect final feedback
\item Prepare experiment report
\item Perform pairwise comparison analysis
\item Prepare analysis report
\end {enumerate}

- Pairwise Comparison Methodology needs to be described
- Downloaded OBS to record experiment sessions, will test it's capability
Describe experiments with users to assess usability, performance etc.
